Comparing GA Part 2

### 2022-02-24 graphs_newt_snakes/Comparing_GA_part_2.Rmd
I am working on an animation that shows clumps of individuals phenotypes over the course of the simulation. I am also trying to make a boxplot of phenotypes and predation

>>>>

## Data as box plots

Here I want to look at some boxplots of the phenotype and predation from the 100,000 generation simulation.

```{r, boxplottinh}
GA_file_100$mean_predation <- GA_file_100$newt_deaths/GA_file_100$Newt_pop_size

GA_file_100$gen_boxy <- round_any(GA_file_100$gen, 1000, f = ceiling) 
ggplot(data = GA_file_100[which(GA_file_100$gen_boxy>=95000),], aes(x = factor(gen_boxy), y = mean_predation)) +
  facet_wrap(~sim)+
  geom_boxplot() +
  xlab("Generation") +
  ylab("mean_predation")
